Democracy, Public Support, and Measurement Uncertainty

### 2021-07-22 paper/dcpo_demsupport.Rmd
update moc models with corrected data.

load(here("data", "pure_cls_ajps.rda")) 
load(here("data", "pure_cls_apsr.rda")) 
load(here("data", "exp_cls_ajps.rda"))
load(here("data", "exp_cls_apsr.rda"))

@@

result_clsAJPS <- readRDS(here("output", "estimates_clsMeanAJPS.RDS"))
result_clsAPSR <- readRDS(here("output", "estimates_clsMeanAPSR.RDS"))
mocresult_pureAJPS <- readRDS(here("output", "estimates_moc_pureAJPS.RDS"))
mocresult_expAJPS <- readRDS(here("output", "estimates_moc_expAJPS.RDS"))
mocresult_pureAPSR <- readRDS(here("output", "estimates_moc_pureAPSR.RDS"))
mocresult_expAPSR <- readRDS(here("output", "estimates_moc_expAPSR.RDS"))

@@

df_pure_clsAjps <- purrr::map(1:900, function(anEntry) {
  pure_cls_ajps[[anEntry]] %>% 
    plm::pdata.frame(index = c("country", "year"))
})

result_pure_clsUncertain  <- map(ls_mod_ajpsCLS[1:2], function(aMod){
  result <- methodComposition1(df_pure_clsAjps,aMod)
})

names(result_pure_clsUncertain) <- c("pooled", "pooled-regime")

result_pure_clsUncertain_gmm  <- map(ls_mod_ajpsCLS[3:4], function(aMod){
  result <- methodComposition2(df_pure_clsAjps,aMod)
})
names(result_pure_clsUncertain_gmm) <- c("gmm", "gmm-regime")

mocresult_pureAJPS <- append(result_pure_clsUncertain, result_pure_clsUncertain_gmm)

saveRDS(mocresult_pureAJPS, file =here("output","estimates_moc_pureAJPS.RDS"))

@@

result_pooled <- bind_rows(
  mutate(result_clsAJPS[["pooled"]][[1]][,1:3], model = "Original"),
  mutate(MOCsumm(mocresult_pureAJPS[["pooled"]]), model = "Uncertainty"),
  mutate(MOCsumm(mocresult_expAJPS[["pooled"]]), model = "Uncertainty+Expanded Data")
) %>% 
  mutate(type = "Pooled")

result_gmm <- bind_rows(
  mutate(result_clsAJPS[["gmm"]][[1]][,1:3], model = "Original"),
  mutate(MOCsumm(mocresult_pureAJPS[["gmm"]]), model = "Uncertainty"),
  mutate(MOCsumm(mocresult_expAJPS[["gmm"]]), model = "Uncertainty+Expanded Data")
) %>% 
  mutate(type = "GMM")

result_pooledAJPS <- bind_rows(result_pooled, result_gmm) %>%
  filter(term != "(Intercept)") %>%
  mutate(
    term = rep(
      c("Democracy\n (t-1)",
        "Democracy\n (t-2)",
        "Support\n (t-1)",
        "Log GDP\n per capita\n (t-1)",
        "GDP per\n capita growth\n (t-1)",
        "Regional\n democracy\n (t-1)",
        "Percent\n Muslim\n (t-1)",
        "Resource\n dependence\n (t-1)"),
      time = 6), 
    type = factor(type, levels = c("Pooled", "GMM")),
    model = factor(model, levels = c("Original", "Uncertainty", "Uncertainty+Expanded Data")))

@@

###########Regime
result_regime <- bind_rows(
  mutate(result_clsAJPS[["pooled-regime"]][[1]][,1:3], model = "Original"),
  mutate(MOCsumm(mocresult_pureAJPS[["pooled-regime"]]), model = "Uncertainty"),
  mutate(MOCsumm(mocresult_expAJPS[["pooled-regime"]]), model = "Uncertainty+Expanded Data")
) %>% 
  mutate(type = "Pooled")

result_regimeGmm <- bind_rows(
  mutate(result_clsAJPS[["gmm-regime"]][[1]][,1:3], model = "Original"),
  mutate(MOCsumm(mocresult_pureAJPS[["gmm-regime"]]), model = "Uncertainty"),
 mutate(MOCsumm(mocresult_expAJPS[["gmm-regime"]]), model = "Uncertainty+Expanded Data")
)%>% 
  mutate(type = "GMM")

result_regimeAJPS <- bind_rows(result_regime, result_regimeGmm) %>%
  filter(term != "(Intercept)") %>%
  mutate(
    term = rep(
      c("Democracy\n (t-1)",
        "Democracy\n (t-2)",
        "Support\n demo only\n (t-1)",
        "Support\n auto only\n (t-1)",
        "Log GDP\n per capita\n (t-1)",
        "GDP per\n capita growth\n (t-1)",
        "Regional\n democracy\n (t-1)",
        "Percent\n Muslim\n (t-1)",
        "Resource\n dependence\n (t-1)"),
      time = 6), 
    type = factor(type, levels = c("Pooled", "GMM")),
    model = factor(model, levels = c("Original","Uncertainty", "Uncertainty+Expanded Data")))
terms2 <- factor(rev(c("Democracy[t-1]",
                       "Democracy[t-2]",
                       "Support[t-1] (democracies~only)",
                       "Support[t-1] (autocracies~only)",
                       "Log~GDP~per~capita[t-1]",
                       "GDP~per~capita~growth[t-1]",
                       "Regional~democracy[t-1]",
                       "Percent~Muslim[t-1]",
                       "Resource~dependence[t-1]")), levels =
                   rev(c("Democracy[t-1]",
                         "Democracy[t-2]",
                         "Support[t-1] (democracies~only)",
                         "Support[t-1] (autocracies~only)",
                         "Log~GDP~per~capita[t-1]",
                         "GDP~per~capita~growth[t-1]",
                         "Regional~democracy[t-1]",
                         "Percent~Muslim[t-1]",
                         "Resource~dependence[t-1]")))
plot_AJPS2 <- dwplot(result_regimeAJPS, dodge_size = 0.8, by_2sd = FALSE) +
  scale_y_discrete(labels = parse(text = levels(terms2))) +
  scale_color_grey(start = 0.4, end = 0.8, guide = guide_legend(reverse = TRUE)) +
  labs(
    title = "",
    subtitle = "Regime Specific"
  ) +
  facet_wrap(~type, scales = "free_x") +
  theme(legend.position = "bottom", 
        legend.title = element_blank())
legend <- get_legend(plot_AJPS2)
plot_AJPS2 <- plot_AJPS2 + theme(legend.position = "none")
grid.arrange(plot_AJPS1, plot_AJPS2, legend, ncol = 1)
```

@@

df_pure_clsAPSR <- purrr::map(1:900, function(anEntry) {
  pure_cls_apsr[[anEntry]] %>% 
    plm::pdata.frame(index = c("country", "year"))
}
)

mocresult_pureAPSR  <- map(ls_mod_apsrCLS, function(aMod){
  result <- methodComposition3(df_pure_clsAPSR,aMod)
})

names(mocresult_pureAPSR) <- c("pooled1", "pooled-regime1", "pooled2", "pooled-regime2",
                                "fd1", "fd-regime1", "fd2", "fd-regime2")

saveRDS(mocresult_pureAPSR, file = here::here("ouput","estimates_moc_pureAPSR.RDS"))

@@

result_ecm1 <- bind_rows(
  mutate(result_clsAPSR[["pooled1"]][[1]][,1:3], model = "Original"),
  mutate(MOCsumm2(mocresult_pureAPSR[["pooled1"]]), model = "Uncertainty"),
  mutate(MOCsumm2(mocresult_expAPSR[["pooled1"]]), model = "Uncertainty+Expanded Data")
) %>% 
  mutate(type = "ECM")

result_fd1 <- bind_rows(
  mutate(result_clsAPSR[["fd1"]][[1]][,1:3], model = "Original"),
  mutate(MOCsumm2(mocresult_pureAPSR[["fd1"]]), model = "Uncertainty"),
  mutate(MOCsumm2(mocresult_expAPSR[["fd1"]]), model = "Uncertainty+Expanded Data")
) %>% 
  mutate(type = "First Difference")

result_APSR1 <- bind_rows(result_ecm1, result_fd1) %>%
  filter(term != "(Intercept)") %>%
  mutate(
    term = c(rep(
      c("Democratic Mood\n (t-1)",
        "Democratic Mood\n (t-2)",
        "Liberal Democracy\n (Difference)",
        "Liberal Democracy\n (t-1)",
        "Log GDP\n per capita\n (Difference)",
        "Log GDP\n (t-1)"),
      time = 3),
      rep(
        c("Liberal Democracy\n (Difference)", 
          "Log GDP\n per capita\n (Difference)"), 
        time = 3
      )),
    type = factor(type,  levels = c("ECM", "First Difference")),
    model = factor(model, levels = c("Original","Uncertainty", "Uncertainty+Expanded Data"))
  )

@@

result_ecmReg1 <- bind_rows(
  mutate(result_clsAPSR[["pooled-regime1"]][[1]][,1:3], model = "Original"),
  mutate(MOCsumm2(mocresult_pureAPSR[["pooled-regime1"]]), model = "Uncertainty"),
  mutate(MOCsumm2(mocresult_expAPSR[["pooled-regime1"]]), model = "Uncertainty+Expanded Data")
) %>% 
  mutate(type = "ECM")

result_fdReg1 <- bind_rows(
  mutate(result_clsAPSR[["fd-regime1"]][[1]][,1:3], model = "Original"),
  mutate(MOCsumm2(mocresult_pureAPSR[["fd-regime1"]]), model = "Uncertainty"),
  mutate(MOCsumm2(mocresult_expAPSR[["fd-regime1"]]), model = "Uncertainty+Expanded Data")
) %>% 
  mutate(type = "First Difference")

result_RegAPSR1 <- bind_rows(result_ecmReg1, result_fdReg1) %>%
  filter(term != "(Intercept)") %>%
  mutate(
    term = c(rep(
      c("Democratic Mood\n (t-1)",
        "Democratic Mood\n (t-2)",
        "Electoral Democracy\n (Difference)",
        "Electoral Democracy\n (t-1)",
        "Minoritarian Democracy\n (Difference)",
        "Minoritarian Democracy\n (t-1)",
        "Log GDP\n per capita\n (Difference)",
        "Log GDP\n (t-1)"),
      time = 3),
      rep(
        c("Electoral Democracy\n (Difference)", 
          "Minoritarian Democracy\n (Difference)",
          "Log GDP\n per capita\n (Difference)"), 
        time = 3
      )),
    type = factor(type,  levels = c("ECM", "First Difference")),
    model = factor(model, levels = c("Original","Uncertainty", "Uncertainty+Expanded Data"))
  )
terms3 <- factor(rev(c("Support[t-1]",
                       "Support[t-2]",
                       "Delta~Electoral~democracy",
                       "Electoral~democracy[t-1]",
                       "Delta~Minoritarian~democracy",
                       "Minoritarian~democracy[t-1]",
                       "Delta~Log~GDP~per~capita",
                       "Log~GDP[t-1]")),
                 levels = rev(c("Support[t-1]",
                                "Support[t-2]",
                                "Delta~Electoral~democracy",
                                "Electoral~democracy[t-1]",
                                "Delta~Minoritarian~democracy",
                                "Minoritarian~democracy[t-1]",
                                "Delta~Log~GDP~per~capita",
                                "Log~GDP[t-1]")))
plot_RegAPSR1 <- dwplot(result_RegAPSR1, dodge_size = 0.8, by_2sd = FALSE) +
  scale_y_discrete(labels = parse(text = levels(terms3))) +
  scale_color_grey(start = 0.4, end = 0.8, guide = guide_legend(reverse = TRUE)) +
  # scale_color_uiowa(name = "", palette = "digitMixed") +
  labs(
    title = "",
    subtitle = "Regime Specified"
  ) +
  facet_wrap(~type, scales = "free_x") + 
  theme(legend.position = "none")

@@

result_ecm2 <- bind_rows(
  mutate(result_clsAPSR[["pooled2"]][[1]][,1:3], model = "Original"),
  mutate(MOCsumm2(mocresult_pureAPSR[["pooled2"]]), model = "Uncertainty"),
  mutate(MOCsumm2(mocresult_expAPSR[["pooled2"]]), model = "Uncertainty+Expanded Data")
) %>% 
  mutate(type = "ECM")

result_fd2 <- bind_rows(
  mutate(result_clsAPSR[["fd2"]][[1]][,1:3], model = "Original"),
  mutate(MOCsumm2(mocresult_pureAPSR[["fd2"]]), model = "Uncertainty"),
  mutate(MOCsumm2(mocresult_expAPSR[["fd2"]]), model = "Uncertainty+Expanded Data")
) %>% 
  mutate(type = "First Difference")

result_APSR2 <- bind_rows(result_ecm2, result_fd2) %>%
  filter(term != "(Intercept)") %>%
  mutate(
    term = c(rep(
      c("Democratic Mood\n (t-1)",
        "Democratic Mood\n (t-2)",
        "Liberal Democracy\n (Difference)",
        "Liberal Democracy\n (t-1)",
        "Log GDP\n per capita\n (Difference)",
        "Log GDP\n (t-1)",
        "Corruption\n (Difference)",
        "Corruption\n (t-1)"
      ),
      time = 3),
      rep(
        c("Liberal Democracy\n (Difference)", 
          "Log GDP\n per capita\n (Difference)",
          "Corruption\n (Difference)"), 
        time = 3
      )),
    type = factor(type,  levels = c("ECM", "First Difference")),
    model = factor(model, levels = c("Original","Uncertainty", "Uncertainty+Expanded Data"))
  )
terms2 <- factor(rev(c("Support[t-1]",
                       "Support[t-2]",
                       "Delta~Liberal~democracy",
                       "Liberal~democracy[t-1]",
                       "Delta~Log~GDP~per~capita",
                       "Log~GDP[t-1]",
                       "Delta~Corruption",
                       "Corruption[t-1]")),
                 levels = rev(c("Support[t-1]",
                                "Support[t-2]",
                                "Delta~Liberal~democracy",
                                "Liberal~democracy[t-1]",
                                "Delta~Log~GDP~per~capita",
                                "Log~GDP[t-1]",
                                "Delta~Corruption",
                                "Corruption[t-1]")))
plot_APSR2 <- dwplot(result_APSR2, dodge_size = 0.8, by_2sd = FALSE) +
  scale_y_discrete(labels = parse(text = levels(terms2))) +
  scale_color_grey(start = 0.4, end = 0.8, guide = guide_legend(reverse = TRUE)) +
  # scale_color_uiowa(name = "", palette = "digitMixed") +
  labs(
    title = "",
    subtitle = "W. Corruption"
  ) +
  facet_wrap(~type, scales = "free_x") +
  theme(legend.position = "none")

@@

result_ecmReg2 <- bind_rows(
  mutate(result_clsAPSR[["pooled-regime2"]][[1]][,1:3], model = "Original"),
  mutate(MOCsumm2(mocresult_pureAPSR[["pooled-regime2"]]), model = "Uncertainty"),
  mutate(MOCsumm2(mocresult_expAPSR[["pooled-regime2"]]), model = "Uncertainty+Expanded Data")) %>% 
  mutate(type = "ECM")

result_fdReg2 <- bind_rows(
  mutate(result_clsAPSR[["fd-regime2"]][[1]][,1:3], model = "Original"),
  mutate(MOCsumm2(mocresult_pureAPSR[["fd-regime2"]]), model = "Uncertainty"),
  mutate(MOCsumm2(mocresult_expAPSR[["fd-regime2"]]), model = "Uncertainty+Expanded Data")) %>% 
  mutate(type = "First Difference")

>>>>

#load(here("data", "pure_cls_ajps.rda")) 
#load(here("data", "pure_cls_apsr.rda")) 
load(here("data", "correct_cls_ajps.rda"))
load(here("data", "correct_cls_apsr.rda")) 
load(here("data", "exp_cls_ajps.rda"))
load(here("data", "exp_cls_apsr.rda"))

@@

result_clsAJPS <- readRDS(here("output", "estimates_clsMeanAJPS.RDS"))
result_clsAPSR <- readRDS(here("output", "estimates_clsMeanAPSR.RDS"))
#mocresult_pureAJPS <- readRDS(here("output", "estimates_moc_pureAJPS.RDS"))
mocresult_correctAJPS <- readRDS(here("output", "estimates_moc_correctAJPS.RDS"))
mocresult_expAJPS <- readRDS(here("output", "estimates_moc_expAJPS.RDS"))
#mocresult_pureAPSR <- readRDS(here("output", "estimates_moc_pureAPSR.RDS"))
mocresult_correctAPSR <- readRDS(here("output", "estimates_moc_correctAPSR.RDS"))
mocresult_expAPSR <- readRDS(here("output", "estimates_moc_expAPSR.RDS"))

@@

#df_pure_clsAjps <- purrr::map(1:900, function(anEntry) {
#  pure_cls_ajps[[anEntry]] %>% 
#    plm::pdata.frame(index = c("country", "year"))
#})

#result_pure_clsUncertain  <- map(ls_mod_ajpsCLS[1:2], function(aMod){
#  result <- methodComposition1(df_pure_clsAjps,aMod)
#})

#names(result_pure_clsUncertain) <- c("pooled", "pooled-regime")

#result_pure_clsUncertain_gmm  <- map(ls_mod_ajpsCLS[3:4], function(aMod){
#  result <- methodComposition2(df_pure_clsAjps,aMod)
#})
#names(result_pure_clsUncertain_gmm) <- c("gmm", "gmm-regime")

#mocresult_pureAJPS <- append(result_pure_clsUncertain, result_pure_clsUncertain_gmm)

#saveRDS(mocresult_pureAJPS, file =here("output","estimates_moc_pureAJPS.RDS"))

df_correct_clsAjps <- purrr::map(1:900, function(anEntry) {
  correct_cls_ajps[[anEntry]] %>% 
    plm::pdata.frame(index = c("country", "year"))
})

result_correct_clsUncertain  <- map(ls_mod_ajpsCLS[1:2], function(aMod){
  result <- methodComposition1(df_correct_clsAjps,aMod)
})

names(result_correct_clsUncertain) <- c("pooled", "pooled-regime")

result_correct_clsUncertain_gmm  <- map(ls_mod_ajpsCLS[3:4], function(aMod){
  result <- methodComposition2(df_correct_clsAjps,aMod)
})
names(result_correct_clsUncertain_gmm) <- c("gmm", "gmm-regime")

mocresult_correctAJPS <- append(result_correct_clsUncertain, result_correct_clsUncertain_gmm)

saveRDS(mocresult_correctAJPS, file =here("output","estimates_moc_correctAJPS.RDS"))

@@

result_pooled <- bind_rows(
  mutate(result_clsAJPS[["pooled"]][[1]][,1:3], model = "Original"),
 # mutate(MOCsumm(mocresult_pureAJPS[["pooled"]]), model = "Uncertainty"),
 mutate(MOCsumm(mocresult_correctAJPS[["pooled"]]), model = "Corrected"),
  mutate(MOCsumm(mocresult_expAJPS[["pooled"]]), model = "Uncertainty+Expanded Data")
) %>% 
  mutate(type = "Pooled")

result_gmm <- bind_rows(
  mutate(result_clsAJPS[["gmm"]][[1]][,1:3], model = "Original"),
  #mutate(MOCsumm(mocresult_pureAJPS[["gmm"]]), model = "Uncertainty"),
  mutate(MOCsumm(mocresult_correctAJPS[["gmm"]]), model = "Corrected"),
  mutate(MOCsumm(mocresult_expAJPS[["gmm"]]), model = "Uncertainty+Expanded Data")
) %>% 
  mutate(type = "GMM")

result_pooledAJPS <- bind_rows(result_pooled, result_gmm) %>%
  filter(term != "(Intercept)") %>%
  mutate(
    term = rep(
      c("Democracy\n (t-1)",
        "Democracy\n (t-2)",
        "Support\n (t-1)",
        "Log GDP\n per capita\n (t-1)",
        "GDP per\n capita growth\n (t-1)",
        "Regional\n democracy\n (t-1)",
        "Percent\n Muslim\n (t-1)",
        "Resource\n dependence\n (t-1)"),
      time = 6), 
    type = factor(type, levels = c("Pooled", "GMM")),
    model = factor(model, levels = c("Original", "Corrected", "Uncertainty+Expanded Data")))

@@

###########Regime
result_regime <- bind_rows(
  mutate(result_clsAJPS[["pooled-regime"]][[1]][,1:3], model = "Original"),
  #mutate(MOCsumm(mocresult_pureAJPS[["pooled-regime"]]), model = "Uncertainty"),
  mutate(MOCsumm(mocresult_correctAJPS[["pooled-regime"]]), model = "Corrected"),
  mutate(MOCsumm(mocresult_expAJPS[["pooled-regime"]]), model = "Uncertainty+Expanded Data")
) %>% 
  mutate(type = "Pooled")

result_regimeGmm <- bind_rows(
  mutate(result_clsAJPS[["gmm-regime"]][[1]][,1:3], model = "Original"),
  #mutate(MOCsumm(mocresult_pureAJPS[["gmm-regime"]]), model = "Uncertainty"),
  mutate(MOCsumm(mocresult_correctAJPS[["gmm-regime"]]), model = "Corrected"),
 mutate(MOCsumm(mocresult_expAJPS[["gmm-regime"]]), model = "Uncertainty+Expanded Data")
)%>% 
  mutate(type = "GMM")

result_regimeAJPS <- bind_rows(result_regime, result_regimeGmm) %>%
  filter(term != "(Intercept)") %>%
  mutate(
    term = rep(
      c("Democracy\n (t-1)",
        "Democracy\n (t-2)",
        "Support\n demo only\n (t-1)",
        "Support\n auto only\n (t-1)",
        "Log GDP\n per capita\n (t-1)",
        "GDP per\n capita growth\n (t-1)",
        "Regional\n democracy\n (t-1)",
        "Percent\n Muslim\n (t-1)",
        "Resource\n dependence\n (t-1)"),
      time = 6), 
    type = factor(type, levels = c("Pooled", "GMM")),
    model = factor(model, levels = c("Original","Corrected", "Uncertainty+Expanded Data")))
terms2 <- factor(rev(c("Democracy[t-1]",
                       "Democracy[t-2]",
                       "Support[t-1] (democracies~only)",
                       "Support[t-1] (autocracies~only)",
                       "Log~GDP~per~capita[t-1]",
                       "GDP~per~capita~growth[t-1]",
                       "Regional~democracy[t-1]",
                       "Percent~Muslim[t-1]",
                       "Resource~dependence[t-1]")), levels =
                   rev(c("Democracy[t-1]",
                         "Democracy[t-2]",
                         "Support[t-1] (democracies~only)",
                         "Support[t-1] (autocracies~only)",
                         "Log~GDP~per~capita[t-1]",
                         "GDP~per~capita~growth[t-1]",
                         "Regional~democracy[t-1]",
                         "Percent~Muslim[t-1]",
                         "Resource~dependence[t-1]")))
plot_AJPS2 <- dwplot(result_regimeAJPS, dodge_size = 0.8, by_2sd = FALSE) +
  scale_y_discrete(labels = parse(text = levels(terms2))) +
  scale_color_grey(start = 0.4, end = 0.8, guide = guide_legend(reverse = TRUE)) +
  labs(
    title = "",
    subtitle = "Regime Specific"
  ) +
  facet_wrap(~type, scales = "free_x") +
  theme(legend.position = "bottom", 
        legend.title = element_blank())
legend <- get_legend(plot_AJPS2)
plot_AJPS2 <- plot_AJPS2 + theme(legend.position = "none")
grid.arrange(plot_AJPS1, plot_AJPS2, legend, ncol = 1)
```

@@

#df_pure_clsAPSR <- purrr::map(1:900, function(anEntry) {
#  pure_cls_apsr[[anEntry]] %>% 
#    plm::pdata.frame(index = c("country", "year"))
#}
#)

#mocresult_pureAPSR  <- map(ls_mod_apsrCLS, function(aMod){
#  result <- methodComposition3(df_pure_clsAPSR,aMod)
#})

#names(mocresult_pureAPSR) <- c("pooled1", "pooled-regime1", "pooled2", "pooled-regime2",
#                                "fd1", "fd-regime1", "fd2", "fd-regime2")

#saveRDS(mocresult_pureAPSR, file = here::here("ouput","estimates_moc_pureAPSR.RDS"))

df_correct_clsAPSR <- purrr::map(1:900, function(anEntry) {
  correct_cls_apsr[[anEntry]] %>% 
    plm::pdata.frame(index = c("country", "year"))
}
)

mocresult_correctAPSR  <- map(ls_mod_apsrCLS, function(aMod){
  result <- methodComposition3(df_correct_clsAPSR,aMod)
})

names(mocresult_correctAPSR) <- c("pooled1", "pooled-regime1", "pooled2", "pooled-regime2",
                                "fd1", "fd-regime1", "fd2", "fd-regime2")

saveRDS(mocresult_correctAPSR, file = here::here("ouput","estimates_moc_correctAPSR.RDS"))

#df_exp_clsAPSR <- purrr::map(1:900, function(anEntry) {
#  exp_cls_apsr[[anEntry]] %>% 
#    plm::pdata.frame(index = c("country", "year"))
#}
#)

#mocresult_expAPSR <- map(ls_mod_apsrCLS, function(aMod){
 # result <- methodComposition3(df_exp_clsAPSR,aMod)
#})

#names(mocresult_expAPSR) <- c("pooled1", "pooled-regime1", "pooled2", "pooled-regime2",
#                                "fd1", "fd-regime1", "fd2", "fd-regime2")
#saveRDS(mocresult_expAPSR, file = here::here("ouput","estimates_moc_expAPSR.RDS"))

@@

result_ecm1 <- bind_rows(
  mutate(result_clsAPSR[["pooled1"]][[1]][,1:3], model = "Original"),
  #mutate(MOCsumm2(mocresult_pureAPSR[["pooled1"]]), model = "Uncertainty"),
  mutate(MOCsumm2(mocresult_correctAPSR[["pooled1"]]), model = "Corrected"),
  mutate(MOCsumm2(mocresult_expAPSR[["pooled1"]]), model = "Uncertainty+Expanded Data")
) %>% 
  mutate(type = "ECM")

result_fd1 <- bind_rows(
  mutate(result_clsAPSR[["fd1"]][[1]][,1:3], model = "Original"),
  #mutate(MOCsumm2(mocresult_pureAPSR[["fd1"]]), model = "Uncertainty"),
  mutate(MOCsumm2(mocresult_correctAPSR[["fd1"]]), model = "Corrected"),
  mutate(MOCsumm2(mocresult_expAPSR[["fd1"]]), model = "Uncertainty+Expanded Data")
) %>% 
  mutate(type = "First Difference")

result_APSR1 <- bind_rows(result_ecm1, result_fd1) %>%
  filter(term != "(Intercept)") %>%
  mutate(
    term = c(rep(
      c("Democratic Mood\n (t-1)",
        "Democratic Mood\n (t-2)",
        "Liberal Democracy\n (Difference)",
        "Liberal Democracy\n (t-1)",
        "Log GDP\n per capita\n (Difference)",
        "Log GDP\n (t-1)"),
      time = 3),
      rep(
        c("Liberal Democracy\n (Difference)", 
          "Log GDP\n per capita\n (Difference)"), 
        time = 3
      )),
    type = factor(type,  levels = c("ECM", "First Difference")),
    model = factor(model, levels = c("Original","Corrected", "Uncertainty+Expanded Data"))
  )

@@

result_ecmReg1 <- bind_rows(
  mutate(result_clsAPSR[["pooled-regime1"]][[1]][,1:3], model = "Original"),
  #mutate(MOCsumm2(mocresult_pureAPSR[["pooled-regime1"]]), model = "Uncertainty"),
  mutate(MOCsumm2(mocresult_correctAPSR[["pooled-regime1"]]), model = "Corrected"),

  mutate(MOCsumm2(mocresult_expAPSR[["pooled-regime1"]]), model = "Uncertainty+Expanded Data")
) %>% 
  mutate(type = "ECM")

result_fdReg1 <- bind_rows(
  mutate(result_clsAPSR[["fd-regime1"]][[1]][,1:3], model = "Original"),
  #mutate(MOCsumm2(mocresult_pureAPSR[["fd-regime1"]]), model = "Uncertainty"),
  mutate(MOCsumm2(mocresult_correctAPSR[["fd-regime1"]]), model = "Corrected"),
  mutate(MOCsumm2(mocresult_expAPSR[["fd-regime1"]]), model = "Uncertainty+Expanded Data")
) %>% 
  mutate(type = "First Difference")

result_RegAPSR1 <- bind_rows(result_ecmReg1, result_fdReg1) %>%
  filter(term != "(Intercept)") %>%
  mutate(
    term = c(rep(
      c("Democratic Mood\n (t-1)",
        "Democratic Mood\n (t-2)",
        "Electoral Democracy\n (Difference)",
        "Electoral Democracy\n (t-1)",
        "Minoritarian Democracy\n (Difference)",
        "Minoritarian Democracy\n (t-1)",
        "Log GDP\n per capita\n (Difference)",
        "Log GDP\n (t-1)"),
      time = 3),
      rep(
        c("Electoral Democracy\n (Difference)", 
          "Minoritarian Democracy\n (Difference)",
          "Log GDP\n per capita\n (Difference)"), 
        time = 3
      )),
    type = factor(type,  levels = c("ECM", "First Difference")),
    model = factor(model, levels = c("Original","Corrected", "Uncertainty+Expanded Data"))
  )
terms3 <- factor(rev(c("Support[t-1]",
                       "Support[t-2]",
                       "Delta~Electoral~democracy",
                       "Electoral~democracy[t-1]",
                       "Delta~Minoritarian~democracy",
                       "Minoritarian~democracy[t-1]",
                       "Delta~Log~GDP~per~capita",
                       "Log~GDP[t-1]")),
                 levels = rev(c("Support[t-1]",
                                "Support[t-2]",
                                "Delta~Electoral~democracy",
                                "Electoral~democracy[t-1]",
                                "Delta~Minoritarian~democracy",
                                "Minoritarian~democracy[t-1]",
                                "Delta~Log~GDP~per~capita",
                                "Log~GDP[t-1]")))
plot_RegAPSR1 <- dwplot(result_RegAPSR1, dodge_size = 0.8, by_2sd = FALSE) +
  scale_y_discrete(labels = parse(text = levels(terms3))) +
  scale_color_grey(start = 0.4, end = 0.8, guide = guide_legend(reverse = TRUE)) +
  # scale_color_uiowa(name = "", palette = "digitMixed") +
  labs(
    title = "",
    subtitle = "Regime Specified"
  ) +
  facet_wrap(~type, scales = "free_x") + 
  theme(legend.position = "none")

@@

result_ecm2 <- bind_rows(
  mutate(result_clsAPSR[["pooled2"]][[1]][,1:3], model = "Original"),
  #mutate(MOCsumm2(mocresult_pureAPSR[["pooled2"]]), model = "Uncertainty"),
  mutate(MOCsumm2(mocresult_correctAPSR[["pooled2"]]), model = "Corrected"),

  mutate(MOCsumm2(mocresult_expAPSR[["pooled2"]]), model = "Uncertainty+Expanded Data")
) %>% 
  mutate(type = "ECM")

result_fd2 <- bind_rows(
  mutate(result_clsAPSR[["fd2"]][[1]][,1:3], model = "Original"),
  #mutate(MOCsumm2(mocresult_pureAPSR[["fd2"]]), model = "Uncertainty"),
  mutate(MOCsumm2(mocresult_correctAPSR[["fd2"]]), model = "Corrected"),
  mutate(MOCsumm2(mocresult_expAPSR[["fd2"]]), model = "Uncertainty+Expanded Data")
) %>% 
  mutate(type = "First Difference")

result_APSR2 <- bind_rows(result_ecm2, result_fd2) %>%
  filter(term != "(Intercept)") %>%
  mutate(
    term = c(rep(
      c("Democratic Mood\n (t-1)",
        "Democratic Mood\n (t-2)",
        "Liberal Democracy\n (Difference)",
        "Liberal Democracy\n (t-1)",
        "Log GDP\n per capita\n (Difference)",
        "Log GDP\n (t-1)",
        "Corruption\n (Difference)",
        "Corruption\n (t-1)"
      ),
      time = 3),
      rep(
        c("Liberal Democracy\n (Difference)", 
          "Log GDP\n per capita\n (Difference)",
          "Corruption\n (Difference)"), 
        time = 3
      )),
    type = factor(type,  levels = c("ECM", "First Difference")),
    model = factor(model, levels = c("Original","Corrected", "Uncertainty+Expanded Data"))
  )
terms2 <- factor(rev(c("Support[t-1]",
                       "Support[t-2]",
                       "Delta~Liberal~democracy",
                       "Liberal~democracy[t-1]",
                       "Delta~Log~GDP~per~capita",
                       "Log~GDP[t-1]",
                       "Delta~Corruption",
                       "Corruption[t-1]")),
                 levels = rev(c("Support[t-1]",
                                "Support[t-2]",
                                "Delta~Liberal~democracy",
                                "Liberal~democracy[t-1]",
                                "Delta~Log~GDP~per~capita",
                                "Log~GDP[t-1]",
                                "Delta~Corruption",
                                "Corruption[t-1]")))
plot_APSR2 <- dwplot(result_APSR2, dodge_size = 0.8, by_2sd = FALSE) +
  scale_y_discrete(labels = parse(text = levels(terms2))) +
  scale_color_grey(start = 0.4, end = 0.8, guide = guide_legend(reverse = TRUE)) +
  # scale_color_uiowa(name = "", palette = "digitMixed") +
  labs(
    title = "",
    subtitle = "W. Corruption"
  ) +
  facet_wrap(~type, scales = "free_x") +
  theme(legend.position = "none")

@@

result_ecmReg2 <- bind_rows(
  mutate(result_clsAPSR[["pooled-regime2"]][[1]][,1:3], model = "Original"),
 # mutate(MOCsumm2(mocresult_pureAPSR[["pooled-regime2"]]), model = "Uncertainty"),
 mutate(MOCsumm2(mocresult_correctAPSR[["pooled-regime2"]]), model = "Corrected"),

  mutate(MOCsumm2(mocresult_expAPSR[["pooled-regime2"]]), model = "Uncertainty+Expanded Data")) %>% 
  mutate(type = "ECM")

result_fdReg2 <- bind_rows(
  mutate(result_clsAPSR[["fd-regime2"]][[1]][,1:3], model = "Original"),
  #mutate(MOCsumm2(mocresult_pureAPSR[["fd-regime2"]]), model = "Uncertainty"),
  mutate(MOCsumm2(mocresult_correctAPSR[["fd-regime2"]]), model = "Corrected"),
  mutate(MOCsumm2(mocresult_expAPSR[["fd-regime2"]]), model = "Uncertainty+Expanded Data")) %>% 
  mutate(type = "First Difference")
